Blocking-resistant communication\\through domain fronting

### 2014-07-31 docs/meek.tex
Note size overhead.
Maybe shouldn't risk burning CloudFlare for other projects.

% Overhead estimate.
As discussed in Section~\ref{sec:trafficanalysis},
the same TLS session is used for many requests,
so the overhead of the TLS handshake is amortized.

@@

CloudFlare (\url{https://www.cloudflare.com/}),
not to be confused with CloudFront,
is a CDN also marketed as protection against
denial-of-service attacks.
It appears that any domain name on CloudFlare
can front for any other, even custom domains;
however it is not obvious which one is best to use as a front.
The front domain needs to be popular
(causing high collateral damage if blocked),
or else the censor may call our bluff and simply block the domain entirely.
It is doubly bad if that happens because not only is circumvention foiled,
some unsuspecting third part has just had their web site blocked.
A solution may be to round-robin through
a pool of domain names;
or to use ``domainless'' fronting that doesn't send SNI.
Though CloudFlare supports domain fronting,
its terms of service~\cite{cloudflare-terms}
seem to prohibit the kind of tunneled proxying that \meek\ does:
\begin{quote}
\textsc{Section 10: Limitation on non-HTML caching}\\
You acknowledge that CloudFlare's Service is offered as a platform to cache and
serve web pages and websites and is not offered for other purposes
\ldots\ you understand and agree to use the Service solely
for the purpose of hosting and serving web pages\ldots
\end{quote}

@@

Protocols vary in their packet lengths;
a censor may block a circumvention protocol if its length distribution
is distinct enough.
Figure~\ref{fig:datalen}
compares the packet length distribution of both sample traffic traces in both directions.
In both cases, about 38\% of packets have an empty payload, mostly ACKs.
There is a small peak at the usual TCP Maximum Segment Size
of 1460 bytes.
The concentration of values near 1418 bytes
may be caused by Google servers' sizing of TLS records so they fit within TCP segments.
% https://github.com/joyent/node/issues/6889
% http://mailman.nginx.org/pipermail/nginx-devel/2013-December/004703.html
Conspicuous in the \meek\ trace are a small number of
frequent packet sizes,
and the lack of a cluster of small payload lengths of around 50 bytes.
Both of these characteristics are probably artifacts
of Tor's fixed cell size and the nearly fixed-size HTTP headers
added by \meekclient\ and \meekserver.

>>>>

% Overhead estimate.
As discussed in Section~\ref{sec:trafficanalysis},
the same TLS session is used for many requests,
so the overhead of the TLS handshake is amortized.
Tor uses fixed-size cells of 514 bytes~\cite[Section~0.2]{tor-spec}.
% 514 → 543 → 957 → 1079

@@

CloudFlare (\url{https://www.cloudflare.com/}),
not to be confused with CloudFront,
is a CDN also marketed as protection against
denial-of-service attacks.
It appears that any domain name on CloudFlare
can front for any other, even custom domains;
however it is not obvious which one is best to use as a front.
The front domain needs to be popular
(causing high collateral damage if blocked),
or else the censor may call our bluff and simply block the domain entirely.
It is doubly bad if that happens because not only is circumvention foiled,
some unsuspecting third part has just had their web site blocked.
A solution may be to round-robin through
a pool of domain names;
or to use ``domainless'' fronting that doesn't send SNI.
% Though CloudFlare supports domain fronting,
% its terms of service~\cite{cloudflare-terms}
% seem to prohibit the kind of tunneled proxying that \meek\ does:
% \begin{quote}
% \textsc{Section 10: Limitation on non-HTML caching}\\
% You acknowledge that CloudFlare's Service is offered as a platform to cache and
% serve web pages and websites and is not offered for other purposes
% \ldots\ you understand and agree to use the Service solely
% for the purpose of hosting and serving web pages\ldots
% \end{quote}

@@

Protocols vary in their packet lengths;
a censor may block a circumvention protocol if its length distribution
is distinct enough.
Figure~\ref{fig:datalen}
compares the packet length distribution of both sample traffic traces in both directions.
In both cases, about 38\% of packets have an empty payload, mostly ACKs.
There is a small peak at the usual TCP Maximum Segment Size
of 1460 bytes.
The concentration of values near 1418 bytes
may be caused by Google servers' sizing of TLS records so they fit within TCP segments.
% https://github.com/joyent/node/issues/6889
% http://mailman.nginx.org/pipermail/nginx-devel/2013-December/004703.html
Conspicuous in the \meek\ trace are a small number of
frequent packet sizes,
and the lack of a cluster of small payload lengths of around 50 bytes.
Both of these characteristics are probably artifacts
of Tor's fixed cell size and the nearly fixed-size HTTP headers
added by \meekclient\ and \meekserver.
% In this trace, packets of 1024 bytes are probably single
% Tor cells and those of 396 are probably empty polling requests.
